Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2018-01-18 manuscript/usses_water_ms.tex
adds SOILWAT appendix and updates ordering in main text. Closes #13

\new{Following the above procedure, we still lacked soil moisture data for March 2012 (observations did not start unitl April) and for a string of days in 2013 during which the soil moisture probes failed take readings.
Therefore, we used a version of the SOILWAT soil moisture model}
\citep{Sala1992a}
\new{that has been specifically designed for semiarid shrublands and grasslands}
\citep{Bradford2014}.
\new{The model was parameterized using generic sagebrush steppe parameters and local soil texture, soil bulk density, and precipitation data}
\citep{Kleinhesselink2017b}.
\new{We used the locally parameterized SOILWAT model to generate daily soil moisture predictions for the duration of the experiment, but only used SOILWAT predictions where there were gaps in our data (Fig. 2B and Appendix X).}

>>>>

\new{Following the above procedure, we still lacked soil moisture data for March 2012 (observations did not start unitl April) and for a string of days in 2013 during which the soil moisture probes failed take readings.
To fill in these gaps, we used a version of the SOILWAT soil moisture model}
\citep{Sala1992a}
\new{that has been specifically designed for semiarid shrublands and grasslands}
\citep{Bradford2014}.
\new{The model was parameterized using generic sagebrush steppe parameters and local soil texture, soil bulk density, and precipitation data}
\citep{Kleinhesselink2017b}.
\new{We used the locally parameterized SOILWAT model to generate daily soil moisture predictions for the duration of the experiment, but only used SOILWAT predictions where there were gaps in our data (Fig. 2B and Appendix X).
SOILWAT predicted daily soil moisture under ambient conditions similar to our control plots.
We applied the same statistical model and procedure described above to estimate soil moisture in drought and irrigation plots based on control plot conditions.}
